# Setup the Computing Environment

## Install R

We recommend install both regular R and the Microsoft R-Open. Even though the later is better optimized, it fails to install packages with compiled code, (see https://github.com/Microsoft/microsoft-r-open/issues/17). The solution is to install packages in regular R and use a shared library directory for both R instances. 

We recommend install R before install Anaconda Python, as the later will pollute the system environment (for instance, it might throw the `libcurl` version error.)

After downloading the source code from https://www.r-project.org: 

```{r build-R, eval=FALSE, engine='bash'}
# configuration
# run ./configure --help to see all available options
./configure --prefix=/apps/R/R-x.y.z --enable-memory-profiling \
    --enable-R-profiling \
    --enable-R-shlib

# build and install R
make 
make install

# Specify the directory for R packages. This is only needed if we 
# want to install Microsoft R-Open as well. 
mkdir -p /apps/R/lib-x.y.z
echo '.libPaths("/apps/R/lib-x.y.z")' >> ~/.Rprofile

# now run R
/apps/R/R-x.y.z/bin/R --version
```

## Install Python 



## Writing Notes with `R::bookdown`

### Create a new book on Github

Follow the steps below to write a book named **Statistical Models**. First initiate the working directory:

```{r init-bookdown, eval=FALSE, engine='bash'}
mkdir StatisticalModels
cd StatisticalModels
```

Create file `StatisticalModels.Rproj`:

    Version: 1.0
    
    RestoreWorkspace: Default
    SaveWorkspace: Default
    AlwaysSaveHistory: Default
    
    EnableCodeIndexing: Yes
    UseSpacesForTab: Yes
    NumSpacesForTab: 2
    Encoding: UTF-8
    
    RnwWeave: knitr
    LaTeX: pdfLaTeX
    
    AutoAppendNewline: Yes
    StripTrailingWhitespace: Yes
    
    BuildType: Website


Create file `index.Rmd`:

    --- 
    title: "Statistical Models"
    author: "Yue Zhao"
    date: "`r Sys.Date()`"
    site: bookdown::bookdown_site
    output: bookdown::gitbook
    documentclass: book
    biblio-style: apalike
    link-citations: yes
    github-repo: giantwhale/StatisticalModels
    description: "Statistical Models"
    ---
    
    # Introduction {-}
    
    omitted ...

Create file `_bookdown.yml`, so `bookdown` knows to output html files to the docs folder (need by github).

    output_dir: "docs"

Now we can start writing notes in `.Rmd` format.
